Automatic Parallelization and Transparent Fault Tolerance\\ (New project paper)

### 2016-04-07 pubs/tfp16/paper.tex
fix label/ref for Fig 2
sync

An informal specification of the mini-Haskell grammar is given in
Figure~\ref{fig:miniHaskell}.  There is significant overlap with STG resulting
from the structural similarities, but the redundancies are included for
completeness.

@@

\\
Program                & $\mathit{prog}$ & ::= & $\mathit{(o|d)decl}_i$ & Object and data defns
\end{tabular}
\label{fig:miniHaskell}
\caption{mini-Haskell syntax}
\end{figure}

Because mini-Haskell was designed to replace STG, it makes sense to talk about
it in terms of the differences between the two and how mini-Haskell is
translated into STG for the back-end.  Here, the differences are given in order
of perceived utility, or importance to someone transitioning from STG to
mini-Haskell.

>>>>

An informal specification of the mini-Haskell grammar is given in
%something really broken
%Figure~\ref{fig:miniHaskell}.  
Figure~2.  
There is significant overlap with STG resulting
from the structural similarities, but the redundancies are included for
completeness.

@@

\\
Program                & $\mathit{prog}$ & ::= & $\mathit{(o|d)decl}_i$ & Object and data defns
\end{tabular}
\caption{mini-Haskell syntax}
\label{fig:miniHaskell}
\end{figure}

Because mini-Haskell was designed to supplement STG for test generation, it
makes sense to talk about it in terms of the differences between the two and
how mini-Haskell is translated into STG for the back-end.  Here, the
differences are given in order of perceived utility, or importance to someone
transitioning from STG to mini-Haskell.
